Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-21 AO_bondedSi.tex
write up the Gaussian Process regression stuff

The three important characteristics of the gaps are their axial extent, their lateral areal extent, and their areal fill factor.  We bored holes in silicon with inductively coupled plasma etching.  We used two different gases with low and high etch rates.  CHF$_3$ on Si exhibited about 0.3 nm/second etch rate, SF$_6$ exhibited about 1 micron/minute.  The area exposed to the process gases was either a 25 mm diameter circle, or a 15 mm $\times$ 20 mm rectangle.  We protected the unexposed areas with thick photoresist.  We achieved etch depths of 15$\pm$5 nm and 4000$\pm$100 nm, as measured with Veeco NT9100 Optical Profiler for the small depth, and Dektak stylus profilometry for the large depth.  Table \ref{tabbondexper} has more information about the bonding samples, and Table \ref{tabPatternFills} lists the properties of the patterns.  The fill factor is defined as the pattern area covered by gaps relative to the total pattern area.  In a second round of experiments, we achieved gap sizes of 14$-$95 nm on four substrates with three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  For measurements taken with the Veeco NT9100 Optical Profiler, uncertainties were constructed by inspecting the histogram of topology, as shown in Figure \ref{figVS20pattern}.  The large-scale distortions were removed from the topology by masking and flattening to ensure that the uncertainties accurately reflect the distribution of measured heights.  The stylus profiliometry measured values were simply assigned an uncertainty of 5\%, which was consistent with our intuition and experience.  Table \ref{tabbondexper} lists part numbers and descriptions for our bonded substrates.

@@

\subsection{Constructing the predicted transmission}
We constructed the predicted transmission for different artificially induced gaps of known dimension and fill factors using the Fabry-P\`{e}rot machinery described in Section \ref{secTheory}, in particular Equation \ref{eqFP}.  For non-unit fill factor, we assume a perfect bond outside of the artifical gap region and average 100\% transmission with the predicted gap transmission, weighted by the estimated fill factor listed in Table \ref{tabPatternFills}.  No attempt was made to verify the delivered fill factor, but since high precision lithographic processes were employed, we assign no uncertainty to the difference between the delivered fill factor and the designed fill factor.  The depth of the meshes has an associated uncertainty listed in Table \ref{tabbondexper}.  We incorporated the uncertainty in the mesh depth in the following way.  We computed the transmission curve for the 1$\sigma$ lower and upper bounds, and plot a filled band marked as the prediction band.  In some cases the IR imaging was unavailable and we had to place the spectrometer aperture on the mesh without being able to confirm the exact location of the meshed area of the substrate.  Our prediction band had to incorporate our uncertainty about whether or not our measurement beam was overlapping the mesh border.  This overlap behaves like a fill factor weighted towards 100\% bonded.

\subsection{Inferring axial extent of gaps from noisy transmission spectra}
We infer the axial extent of the gaps with correlated measurement uncertainties using Gaussian Processes.

\subsection{Spectra of direct bonded Si with known gap sizes}
Figures \ref{figVG03full} to \ref{figVG12_f50} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.

>>>>

The three important characteristics of the gaps are their axial extent, their lateral areal extent, and their areal fill factor.  We bored holes in silicon with inductively coupled plasma etching.  We used two different gases with low and high etch rates.  CHF$_3$ on Si exhibited about 0.3 nm/second etch rate, SF$_6$ exhibited about 1 micron/minute.  The area exposed to the process gases was either a 25 mm diameter circle, or a 15 mm $\times$ 20 mm rectangle.  We protected the unexposed areas with thick photoresist.  We achieved etch depths of 15$\pm$5 nm and 4000$\pm$100 nm, as measured with Veeco NT9100 Optical Profiler for the small depth, and Dektak stylus profilometry for the large depth.  Table \ref{tabbondexper} has more information about the bonding samples, and Table \ref{tabPatternFills} lists the properties of the patterns.

The fill factor is defined as the pattern area covered by gaps relative to the total pattern area.  In a second round of experiments, we achieved gap sizes of 14$-$95 nm on four substrates with three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  No attempt was made to verify the delivered fill factor, but since high precision lithographic processes were employed, we assign no uncertainty to the difference between the delivered fill factor and the designed fill factor.  For measurements taken with the Veeco NT9100 Optical Profiler, uncertainties were constructed by inspecting the histogram of topology, as shown in Figure \ref{figVS20pattern}.  The large-scale distortions were removed from the topology by masking and flattening to ensure that the uncertainties accurately reflect the distribution of measured heights.  The stylus profiliometry measured values were simply assigned an uncertainty of 5\%, which was consistent with our intuition and experience.  Table \ref{tabbondexper} lists part numbers and descriptions for our bonded substrates.

@@

\subsection{Inferring axial extent of gaps from noisy transmission spectra}
We infer the axial extent of gaps from their noisy transmission spectra.  We use a Bayesian inference technique.  First we define a mixture model in which the observed normalized gap spectrum $T_{obs}$ is composed of a sum of a spectrum through a gap of axial extent $d$, and a spectrum through a perfect bond:

\begin{equation}
	T_{mix} = f T_{e} + (1-f) \label{eqnMix}
\end{equation}

where $f$ is the areal fill factor of the region exhibiting a finite gap size, and $1-f$ is therefore the areal fill factor of the perfectly bonded area.  $T_e$ is defined in equation \ref{eqn:Tetalon}.  The only free parameters in Equation \ref{eqnMix} are $d$ and $f$.  Both of these parameters are fixed in our direct bonded Si wafers with synthetic gaps, and are listed in Table \ref{tabPatternFills}.  These synthetic imbedded gaps therefore offer an excellent test of our ability to recover the gap axial extent $d$ and areal fill factor $f$ (Section \ref{secKnownGaps}).

Equipped with an observed spectrum and our mixture model, we constructed the Likelihood function \verb|\cite{SomeStatisticsBook}|, $\mathcal{L} = p(T_{obs} | d, f)$.  The measurement errors are not assumed to be independent and identically distributed, and in fact are strongly correlated as discussed in Section \verb|\ref{sectionAboutErrors}|.  To handle the correlated measurement errors we use Gaussian Processes \verb|\cite{RasmussenAndWilliams, DFM}|.  The Gaussian Process takes into account the unknown but finite covariance structure by introducing a covariance matrix, $\boldsymbol{C}$ whose elements represent the correlations of each sample $i$ with every other sample $j$.  We parameterize the covariance matrix elements in the following way:

\begin{equation}
	C_{ij} = \sigma^2_{i}\delta_{ij}+a^2\exp{(-\frac{(\lambda_i-\lambda_j)^2}{2l^2})} \label{eqnGPkernel}
\end{equation}

where $\delta_{ij}$ is the Kronecker delta, and $\sigma_i$ are the independent measurement uncertainties on the $i^{\mathrm{th}}$ data point. For simplicity, we adopt values from Table \ref{tabCary5000pars} for single and double beam modes respectively.  This assumption of homoscedasticity is fairly safe, since the correlated errors dominate in comparison to individual measurement errors.  The parameter $l$ controls the correlation length, and $a$ controls the amplitude of the noise.  We do not know $a$ nor $l$ and they are, in general, different for each measurement.  The value of $a$ should be close to the mean drift reported in Table \ref{tabCary5000pars}.  The value of $l$ could be small (tens of nm) to capture local variation attributable to atmospheric air absorption, or large (thousands of nm) to capture global features attributable to lamp drift.  We allow both $a$ and $s$ to be free parameters in our fitting procedure.

We set our priors \verb|\cite{someStatisticsBook}| on $\ln{a}$, $\ln{s}$, $d$, and $f$ as uniform over a wide range of values consistent with visual inspection of each spectrum.  The final un-normalized posterior probability function, expressed as a natural logarithm is:

\begin{equation}
	\ln{p(d,f,a,s|\lambda, T_{obs}, \sigma)} \propto \ln{p(d,f,a,s)} -0.5\;\boldsymbol{r^\intercal}\boldsymbol{C^{-1}}\boldsymbol{r}} -0.5 \ln{\det{\boldsymbol{C}}} \label{eqnPosterior}
\end{equation}

where the residual vector $\boldsymbol{r}$ is the data $T_{obs}$ minus the model $T_{mix}$.  We produce posterior samples with Markov Chain Monte Carlo (MCMC).  Specifically, we implemented \texttt{emcee}\footnote{https://github.com/dfm/emcee}\cite{emcee}, with 32 walkers, hundreds of burn-in samples, and 600-1000 iterations.  We initialized the walkers in the vicinity of our best guess for parameters based on visual inspection of the observed normalized Transmission spectra.  Figures \ref{figVG03full, figVG03part, figVG12_corner} show examples of posterior samples including corner plots of the interesting physical parameters $d$ and $f$.

\subsection{Spectra of direct bonded Si with known gap sizes}
\label{secKnownGaps}
Figures \ref{figVG03full} to \ref{figVG12_f50} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.
